---
title: "R Final Project, Juliet, Charlie, and Devya"
format: html
editor: visual
---

## Ski Jumping Results

Our data set is the Results of (almost) all important ski jumping competitions from 2009 to now. The observations contain standard information about every jump - style points, distance, take-off speed, wind etc.

## Research Questions:

1.  How strong is the correlation between distance and style marks?

 juliet
 Updated upstream

    ```{r}
    library(dplyr)
    library(tidyverse)
    ```

    ```{r}
    Rawresults <- all_results
    CleanResults <- Rawresults %>%
      rename("TotalPoints" = points, #Rename variable columns
             "WindSpeed" = speed,
             "Distance" = dist,
             "Points_DistWind" = dist_points,
             "JudgeA" = note_1,
             "JudgeB" = note_2,
             "JudgeC" = note_3,
             "JudgeD" = note_4,
             "JudgeE" = note_5,
             "StylePoints" = note_points) %>%  
      mutate(AverageStylePoints = (JudgeA+JudgeB+JudgeC+JudgeD+JudgeE)/5) %>% #Add a column for average style points from judges
      filter(TotalPoints!="NA") %>% #Filter out empty columns
      filter(WindSpeed!="NA") %>% 
      filter(Distance!="NA") %>% 
      filter(Points_DistWind!="NA") %>% 
      filter(JudgeA!="NA") %>%
      filter(JudgeB!="NA") %>%
      filter(JudgeC!="NA") %>%
      filter(JudgeD!="NA") %>%
      filter(JudgeE!="NA")  %>% 
      filter(wind!="NA") %>% 
      filter(wind_comp!="NA") %>% 
      filter(gate_points!="NA") %>% 
      filter(bib!="") %>% 
      filter(loc!="NA") %>% 
      filter(Unnamed..0!="NA") %>% 
      filter(Distance<=150) #Filter distances of less than or equal to 150 meters

    #Plot the relationship between the two variables
    plot(Distance~AverageStylePoints, data = CleanResults, pch = 16, col = "red") 
    skiLm <- lm(Distance~AverageStylePoints, data = CleanResults) #Create a linear model for the two variables
    summary(skiLm) #Correlation = (R^2)^1/2 = 0.495
    ```

 main
2.  Can we create a model that predicts the performance/distance of an athlete in a given competition?

    ```{r}
    library(dplyr)
    library(tidyverse)
    ```

    ```{r}
    Rawresults <- all_results
    CleanResults <- Rawresults %>%
      rename("TotalPoints" = points, #Rename variable columns
             "WindSpeed" = speed,
             "Distance" = dist,
             "Points_DistWind" = dist_points,
             "JudgeA" = note_1,
             "JudgeB" = note_2,
             "JudgeC" = note_3,
             "JudgeD" = note_4,
             "JudgeE" = note_5,
             "StylePoints" = note_points) %>%  
      mutate(AverageStylePoints = (JudgeA+JudgeB+JudgeC+JudgeD+JudgeE)/5) %>% #Add a column for average style points from judges
      filter(TotalPoints!="NA") %>% #Filter out empty columns
      filter(WindSpeed!="NA") %>% 
      filter(Distance!="NA") %>% 
      filter(Points_DistWind!="NA") %>% 
      filter(JudgeA!="NA") %>%
      filter(JudgeB!="NA") %>%
      filter(JudgeC!="NA") %>%
      filter(JudgeD!="NA") %>%
      filter(JudgeE!="NA")  %>% 
      filter(wind!="NA") %>% 
      filter(wind_comp!="NA") %>% 
      filter(gate_points!="NA") %>% 
      filter(bib!="") %>% 
      filter(loc!="NA") %>% 
      filter(Unnamed..0!="NA") %>% 
      filter(Distance<=150) #Filter distances of less than or equal to 150 meters

    #Plot the relationship between the two variables
    plot(Distance~AverageStylePoints, data = CleanResults, pch = 16, col = "red") 
    skiLm <- lm(Distance~AverageStylePoints, data = CleanResults) #Create a linear model for the two variables
    summary(skiLm) #Correlation = (R^2)^1/2 = 0.495
    ```

2.  What is the correlation of Wind Speed and Distance? \

```{r}
#Load the packages
library(ggplot2)

#Plot the relationship between Wind Speed and Distance
ggplot(CleanResults, aes(x = Distance, y = WindSpeed)) +
  geom_point(color = "blue") +
  labs(title = "Scatter Plot of Distance vs Wind Speed",
       x = "Distance", y = "Wind Speed")

ggplot(CleanResults, aes(x = WindSpeed, y = Distance)) +
  geom_point(color = "blue", size = 2) +
  geom_smooth(method = "lm", se = FALSE, color = "red") + # Add linear regression line
  labs(title = "Relationship Between Distance and Wind Speed",
       x = "Wind Speed",
       y = "Distance") +
  theme_minimal()


```
 Stashed changes

\
